\documentclass{resume}

\begin{document}

    \begin{header}

        \fontsize{25 pt}{25 pt}\selectfont Gage Rowden, M.S.\\
        \vspace{5 pt}
        \normalsize
        % \mbox{St. Paul, MN}
        % \AND
        \mbox{\hrefWithoutArrow{mailto:gage.rowden1145@gmail.com}{\faEnvelope{ }gage.rowden1145@gmail.com}}
        \AND
        \mbox{\hrefWithoutArrow{tel:+1-806-577-8008}{\faPhone{ }+1-806-577-8008}}
        \AND
        \mbox{\hrefWithoutArrow{https://orcid.org/0000-0002-7517-0480}{\faOrcid{ }orcid.org}}
        \AND
        \mbox{\hrefWithoutArrow{https://www.linkedin.com/in/gagerowden}{\faLinkedin{ }gagerowden}}
        \AND
        \mbox{\hrefWithoutArrow{https://github.com/gage1145}{\faGithub{ }gage1145}}
        % \AND
        % \mbox{\hrefWithoutArrow{https://ganymede1.bandcamp.com}{\faBandcamp{ }ganymede1}}
        % \AND
        % \mbox{\hrefWithoutArrow{https://open.spotify.com/artist/23DyBlyjDtXfYo333RBWj7?si=wZcmKk7hQICzxbMIfN2bnQ}{\faSpotify{ }Ganymede}}
        % \AND
        % \mbox{\hrefWithoutArrow{https://www.facebook.com/gage1145}{\faFacebook{ }gage1145}}
        % \AND
        % \mbox{\hrefWithoutArrow{https://www.instagram.com/ganymede_music}{\faInstagram{ }ganymede\_music}}

    \end{header}

    \vspace{5 pt - 0.3 cm}

    \section{Professional Summary}
        \begin{centering}
        \Large{Data scientist and R\&D specialist with a strong foundation in molecular biology and software development. Experienced in building automated data pipelines, custom R packages, and laboratory systems to streamline diagnostics and research.}
        
        \end{centering}

    \section{Experience}

        \begin{twocolentry}{Jan 2024--present}
            \textbf{Lead Data Scientist}, Priogen Corporation --- St.\ Paul, MN
        \end{twocolentry}
        \begin{onecolentry}
            \begin{highlights}
                \item Designed and optimized data analysis workflows to efficiently process high-throughput datasets.
                \item Built a Django-based LIMS that streamlined client data handling and automated result reporting.
                % \item Contributed to multiple projects which lead to the development of intellectual property.
                \item Established standard operating procedures to enhance lab consistency and quality.
                \item Integrated version control across all projects, ensuring reproducibility and streamlined collaboration.
                % \item Outfitted the diagnostic laboratory, optimizing for high-performance testing and analysis.
            \end{highlights}
        \end{onecolentry}

        \begin{twocolentry}{Aug 2022--present}
            \textbf{Researcher IV}, MNPRO, University of Minnesota --- St.\ Paul, MN
        \end{twocolentry}
        \begin{onecolentry}
            \begin{highlights}
                \item Co-authored 17 manuscripts, including two first-author publications.
                \item Developed a custom R package and automation scripts to optimize data analysis and processing.
                \item Led the expansion of laboratory space, improving research capacity and workflow efficiency.
                % \item Designed and implemented a robust accession system for managing large laboratory inventory.
                \item Provided expert consultation on RT-QuIC and related diagnostic tests for research collaborators.
                % \item Aided in field collection of prion-infected samples, ensuring proper handling and documentation.
            \end{highlights}
        \end{onecolentry}

    \section{Skills}

        % \subskill{Computational Skills}
        \begin{skills}
            \item Amazon Web Services
            \item R \& Tidyverse
            \item R package development
            \item Quarto
            % \item Shiny
            \item Python
            \item Django
            \item SQL
            \item Bash
            \item Data visualization
            % \item \LaTeX
            \item Git \& GitHub
            \item GitHub Actions
            \item Data wrangling
            % \item Bioinformatics
            \item Statistical analysis
        % \end{skills}

        % \subskill{Molecular Biology \& Biochemistry}
        % \begin{skills}
            \item Recombinant DNA technology
            \item DNA cloning
            \item DNA sequencing
            \item PCR techniques
            \item Protein expression/purification
            \item Protein characterization
            \item Western blotting
            % \item Liquid chromatography
            % \item Gas chromatography
            % \item Mass spectrometry
            \item RT-QuIC
            % \item Prion research
            % \item Cell line maintenance
            % \item Bacterial culturing
            % \item Biosafety Level 2 \& 3
            % \item Biosafety Level 3
        % \end{skills}

        % \subskill{Additional Skills}
        % \begin{skills}
            % \item Scientific writing \& publishing
            % \item Project management
            % \item Research ethics
            % \item Public speaking
            % \item Teaching
        \end{skills}
    
    \section{Education}
        \begin{twocolentry}{
            Sep 2011--May 2016\\
            Sep 2016--May 2018
        }
            \textbf{M.S. in Biotechnology}, Texas Tech University \\
            \textbf{B.S. in Biology}, Texas Tech University
        \end{twocolentry}

    \section{Software Projects}
        \begin{software}{\href{https://github.com/gage1145/quicR}{github.com/gage1145/quicR}}
            \textbf{quicR: An R Library for Streamlined Data Handling of RT-QuIC Assays}
        \end{software}
        \begin{highlights}
            \item Developed an R package for the extraction, manipulation, and analysis of RT-QuIC data.
            \item Tools Used: R, Tidyverse, RTools, Git, GitHub
        \end{highlights}

        \begin{software}{\color{primaryColor}{proprietary}}
            \textbf{PriLIMS: A Priogen Laboratory Information Management System}
        \end{software}
        \begin{highlights}
            \item Designed and implemented a Django framework LIMS for Priogen Corp.
            \item Tools Used: Python, Django, SQL, AWS, Bash, Git, GitHub
        \end{highlights}

    \section{First Author Publications}
        \begin{samepage}
            \pub{2025}
            {quicR: An R Library for Streamlined Data Handling of RT-QuIC Assays}
            {\me, Peter A Larsen}
            {10.2139/ssrn.5188757}

            \pub{2023}
            {Standardization of data analysis for RT-QuIC-based detection of chronic wasting disease}
            {\me, \textit{et al}}
            {10.3390/pathogens12020309}
        \end{samepage}

    % \section{Consultation}

    %     Creighton University

\end{document}