\documentclass[11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage{helvet}
\usepackage{datetime}
\usepackage[USenglish]{isodate}
\usepackage{fancyhdr}

% Font and header
\titleformat{\section}{\normalsize\bfseries}{\thesection}{1em}{}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue,
}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\thepage}

\begin{document}

    \fontfamily{phv}\selectfont

    % Title block
    \begin{center}
        {\LARGE\textbf{Gage Rowden, M.S.}}\\
        \vspace{2pt}
        \textit{Lead Technical R\&D Scientist, Priogen Corporation}\\
        % \vspace{2pt}
        % St.\ Paul, MN \quad|\quad\href{mailto:gager@priogen.bio}{gager@priogen.bio}\\
        \vspace{8pt}
        \textbf{\Large Responsibilities Overview} \\
        \cleanlookdateon\textit{\today}
    \end{center}

    \vspace{0.5cm}

    \section*{Data Analysis \& Pipeline Development}
    \begin{itemize}
        \item Design and maintain automated pipelines for processing high-throughput experimental data.
        \item Develop custom scripts for data cleaning, transformation, and statistical analysis.
        \item Implement reproducible workflows using Git and GitHub Actions.
        \item Generate interactive visualizations and reports for internal teams, external partners, and clients.
    \end{itemize}

    \section*{Scientific \& Technical Leadership}
    \begin{itemize}
        \item Oversee experimental design strategies in collaboration with R\&D and service-side leadership.
        \item Provide scientific direction for assay development and optimization.
        \item Troubleshoot and resolve experimental or data quality issues.
        \item Align data analytics efforts with diagnostic objectives and regulatory expectations.
    \end{itemize}

    \section*{Infrastructure}
    \begin{itemize}
        \item Manage internal systems for accessioning, tracking, and analyzing diagnostic data.
        \item Maintain and update SOPs, documentation, and analysis protocols.
        \item Design database infrastructure to support scalable and efficient data management and reporting.
    \end{itemize}

    \section*{Project \& Information Management}
    \begin{itemize}
        \item Act as a project liaison between the service lab, R\&D lab, leadership, and stakeholders.
        \item Coordinate version control across projects to ensure consistent reproducibility.
        \item Manage timelines and deliverables across concurrent data-driven projects.
    \end{itemize}

    \section*{Collaboration \& Mentorship}
    \begin{itemize}
        \item Train and mentor junior scientists in lab operations and analysis workflows.
        \item Facilitate cross-functional collaboration between company departments.
        \item Lead data review sessions to align research and services with company priorities.
    \end{itemize}

\end{document}
